Cosmic Web

### 2014-01-31 paper/main.tex
describing the algorithm

>>>>

\subsection{Cosmic web identification}
The web finding algorithm is based on the tidal tensor computed as the
Hessian of the  gravitational potential field

\begin{equation}
T_{ij} = \frac{\partial^2 \psi}{\partial r_i \partial r_j}, 
\end{equation}
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates.

This tensor is real and symmetric, which means that can be
diagonalized. We note the eigenvalues $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If the three, two, one or zero eigenvalues are larger than this threshold the region es classified as peak, filament, sheet or void, respectively.

In \cite{Tweb} we perform a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. We find that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. In this paper we choose the value of $\lambda_{\rm
  th}=0.3$. We have veryfied that the main trends reported in this
paper are unsensitive to the choice of that parameter, as long as it
is in the range already quoted.

The algorithm to compute the potential is grid based. First we
interpolate the potential into a cubic grid and smooth it with a
gaussian kernel. Then we obtain the gravitational potential and use
finite differences to compute the Hessian at every point in the
grid. Physically speaking, the cosmic web features are scale
dependent and the grid size has to be chosen with respect to the
physical scales of the problem at hand.

In our case we have used a grid size on and a gaussian smoothing with
two times larger as the typical separation between the two
halos in the Local Group. The objective is to have both halos in the
pair a common environment. In this paper we use a grid spacing of
$s=1.024$ \hMpc, corresponding to a $256^3$ grid in the Bolshoi
volume. The scale for the gaussian smoothing uses the same value.
